### 2019-11-22 paper_lap/04nprelim.tex
updates

The Nystr\"{o}m method proceeds as follows. We begin by constructing a discretization of the boundary $\Gamma$ with nodes $s_1,\dots,s_N,$ and weights $w_1,\dots,w_N,$ which enable interpolation of the left- and right-hand sides of the boundary integral equation
\begin{align}\label{eqn:numpreint}
f(t) = -\sigma(t) + \int_0^L k(t,s) \,\sigma(t)\, {\rm d} t
\end{align}
with precision $\epsilon.$ Once these nodes and weights have been generated we proceed by enforcing equality of (\ref{eqn:numpreint}) at the discretization nodes, which yields the system of equations
\begin{align}
f(s_i) \sqrt{w_i} = -\pi \sigma(s_i)\sqrt{w_i} +  \sqrt{w_i}\int_0^L K(\gamma(s_i),\gamma(t))\, \sigma(t)\,{\rm d}t,\quad i=1,\dots,N. \label{eqn_1std}
\end{align}
We note that scaling by the square root of the weights in the above equation is equivalent to solving the problem in the $L^2$ sense, and results in discretized operators with condition numbers which are close to those of the original physical systems \cite{bremer3}. The new unknowns are $\sigma_i = \sigma(s_i) \sqrt{w_i},$ $i=1,\dots,N.$ Next, for each interpolation node $s_i$ we find a collection of weights $W_{ij}$ such that
\begin{align}
\left|\int_0^L K(\gamma(s_i),\gamma(t))\, \sigma(t)\,{\rm d}t- \sum_{j=1}^N W_{ij} \sigma_j\, \sqrt{w_j} \right| < \epsilon,
\end{align}
resulting in the linear system
\begin{align}
  -\pi \sigma_i +  \sum_{j=1}^N W_{ij} \sigma_j \sqrt{w_i w_j}=f(s_i) \sqrt{w_i},\quad i,j=1,\dots,N. 
\end{align}

@@

\begin{definition}\label{def:seps}
Let $S_\epsilon \subset L^2([0,L])$ denote the set of functions which can be interpolated from their values at the $N$ discretization nodes to any point in $[0,L]$ with an $L^2$ accuracy of $\epsilon.$ That is to say that for $f \in S_\epsilon$ if $\tilde{f}:[0,L] \to \mathbb{R}$ denotes the function obtained by interpolating using the values $f(s_1),\dots,f(s_N)$ then $\|f -\tilde{f}\|_{L^2} < \epsilon.$ 
\end{definition}

@@

\subsection{Discretization of the Neumann problem}
In principle a similar method could be employed to discretize the Neumann boundary integral equations. Unfortunately, the singular nature of the powers (the smallest in the expansion given in Theorem \ref{thm_cord} lies in the range $(-1/2,0)$) makes it difficult to produce universal discretizations and quadratures which work for large ranges of angles. When the above method is run on these problems, discretization nodes tend to accumulate close to the corner (within $10^{-14}$). Apart from posing certain numerical challenges, it also makes the task of finding suitable quadrature formulae difficult. Instead a different set of discretization nodes and a different set of quadrature nodes can be constructed for each angle, though this would significantly increase the precomputation cost.

>>>>

The Nystr\"{o}m method proceeds as follows. We begin by constructing a discretization of the boundary $\Gamma$ with nodes $s_1,\dots,s_N,$ and weights $w_1,\dots,w_N,$ which enable interpolation of the left- and right-hand sides of the boundary integral equation
\begin{align}\label{eqn:numpreint}
f(s) = -\sigma(s) + \int_0^L k(t,s) \,\sigma(t)\, {\rm d} t
\end{align}
with precision $\epsilon.$ In other words, given $f(s_i),-\sigma(s_i) + \int_0^L k(t,s_i) \,\sigma(t)\, {\rm d} t,$ for $i=1,\dots,N,$ the values $f(s)$ and $-\sigma(s) + \int_0^L k(t,s) \,\sigma(t)\, {\rm d} t$ can be obtained for all $0 \le s \le L$ to within $\epsilon.$

Once these nodes and weights have been generated we proceed by enforcing equality of (\ref{eqn:numpreint}) at the discretization nodes, which yields the system of equations
\begin{align}
f(s_i) \sqrt{w_i} = -\sigma(s_i)\sqrt{w_i} +  \sqrt{w_i}\int_0^L k(t,s_i)\, \sigma(t)\,{\rm d}t,\quad i=1,\dots,N. \label{eqn_1std}
\end{align}
We note that scaling by the square root of the weights in the above equation is equivalent to solving the problem in the $L^2$ sense, and results in discretized operators with condition numbers which are close to those of the original physical systems \cite{bremer3}. The new unknowns are $\sigma_i = \sigma(s_i) \sqrt{w_i},$ $i=1,\dots,N.$ Next, for each interpolation node $s_i$ we find a collection of weights $W_{ij}$ such that
\begin{align}
\left|\int_0^L k(t,s_i)\, \sigma(t)\,{\rm d}t- \sum_{j=1}^N W_{ij} \sigma_j\, \sqrt{w_j} \right| < \epsilon,
\end{align}
resulting in the linear system
\begin{align}
  -\sigma_i +  \sum_{j=1}^N W_{ij} \sigma_j \sqrt{w_i w_j}=f(s_i) \sqrt{w_i},\quad i,j=1,\dots,N. 
\end{align}

@@

\begin{definition}\label{def:seps}
Let $S_\epsilon \subset L^2([0,L])$ denote the set of functions which can be interpolated from their values at the $N$ discretization nodes to any point in $[0,L]$ with a relative $L^2$ accuracy of $\epsilon.$ That is to say that for $f \in S_\epsilon$ if $\tilde{f}:[0,L] \to \mathbb{R}$ denotes the function obtained by interpolating using the values $f(s_1),\dots,f(s_N)$ then $\|f -\tilde{f}\|_{L^2} < \epsilon.$ 
\end{definition}

@@

\subsection{Discretization of the Neumann problem}
In principle a similar method could be employed to discretize the Neumann boundary integral equations. Unfortunately, the singular nature of the powers (the smallest in the expansion given in Theorem \ref{thm_cord} lies in the range $(-1/2,0)$) makes it difficult to produce universal discretizations and quadratures which work for large ranges of angles. When the above method is run on these problems, discretization nodes tend to accumulate close to the corner (within $10^{-14}$). Apart from posing certain numerical challenges, it also makes the task of finding suitable quadrature formulae difficult. Instead, a different set of discretization nodes and a different set of quadrature nodes can be constructed for each angle, though this would significantly increase the precomputation cost.
